%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer II} % Job title
    {Encora Inc. - Accruent} % Organization
    {Seoul, S.Korea} % Location
    {Jun. 2018 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed highly reusable components in a shared library for usage across multiple projects within the organization}
        \item {Worked migrating a 25 years old CMMS built as an XBapClient to React}
        \item {Implemented a BFF architecture design to couple new CMMS frontend to legacy backend built on WCF}
        \item {Lead and participate in SCRUM ceremonies}
      \end{cvitems}
    }

    %---------------------------------------------------------
  \cventry
  {Software Engineer I} % Job title
  {Encora Inc. - Amazon} % Organization
  {Cali, Colombia} % Location
  {Jul. 2022 - Feb. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Provided support to applications ecosystem, all hosted on AWS}
      \item {Changed client-side to server-side pagination and filtering to improved web apps performance}
      \item {Implemented responsive behaviour on React Native components}
      \item {Analized and solved problems related to data fetching on DynamoDB}
      \item {Used AWS Amplify to provision backend services and infrastructure}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Software Engineer I} % Job title
  {Encora Inc. - Internal Projects} % Organization
  {Cali, Colombia} % Location
  {Aug. 2021 - Jul. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implemented full page table views with pagination, search and filters on React with AntD}
      \item {Created REST API endpoints in .NET 5.0 with full CRUD operations}
      \item {Researched and did a POC on Elsa Workflows library}
      \item {Standarized front-end complex components to gather business critical information}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Fullstack Dev} % Job title
  {Freelance} % Organization
  {Cali, Colombia} % Location
  {Aug. 2021 - Jan. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Design and document client-server app solution on UML}
      \item {Implement frontend project with React and responsive features}
      \item {Develop backend project on NodeJs and PostgreSQL}
      \item {Configure NGIX as reverse proxy to allocate backend and frontend on the same server with the same domain}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Data Analist} % Job title
  {Freelance} % Organization
  {Cali, Colombia} % Location
  {Aug. 2021 - Jan. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Undestand and extract data from a PostgreSQL database using Pypika on Python}
      \item {Transform data with Pandas and Numpy}
      \item {Export data and create reports on PowerBI}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Software Engineer I - Amazon} % Job title
  {Avantica Technologies S.A.S.} % Organization
  {Cali, Colombia} % Location
  {Jan. 2021 - Aug. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implement an ecosystem of application to support logistics operations. Two mobile apps, both for Android and IOS, and two web apps}
      \item {Implemented full mobile apps flows followgin UX/UI desings on Figma}
      \item {Modified pipelines configurations and instructions for both Android, on AWS CodePipeline, and iOS, on Jenkis}
      \item {Team work and collaboration to analyze and plan user stories using Jira as project management tool}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {Avantica Technologies S.A.S.} % Organization
    {Cali, Colombia} % Location
    {Jul. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop full front‐end features with NextJs as SSR framework for React}
        \item {Develop REST endpoints in NodeJs using Sequelize ORM for PostgreSQL}
        \item {Improved SQL database schema to meet chaging design requirements}
        \item {Improved REST API performance and usage}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
